Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-16 paper/paper.Rmd
expand on the downsides of buffer methods

<!-- spcv buffer: discards observations, LOO very expensive -->
Method `"spcv_buffer"` makes use of the removal of observations to reduce the influence of spatial autocorrelation between train and test set.
This can be a pretty effective way to reduce autocorrelation but also requires to discard many observations and comes with the downsides of a LOO-CV: many model fits which can be computationally very demanding and the results inheriting a high variance due to the high differences in the test sets (also commonly known as the "bias-variance tradeoff" [@wahba1998; @blockCV].

>>>>

<!-- spcv buffer and spcv disc: discards observations, LOO very expensive -->
Methods `"spcv_buffer"` and `"spcv_disc"` (optionally) make use of the removal of observations to reduce the influence of spatial autocorrelation between train and test set.
This can be a pretty effective way to reduce autocorrelation but also requires to discard many observations.
In addition it comes with the downsides of a LOO-CV: many model fits which can be computationally very demanding and the results inheriting a high variance due to the high differences in the test sets (also commonly known as the "bias-variance tradeoff" [@wahba1998; @blockCV].
If a large buffer size is chosen relatively to the overall study area size, a large portion of it will not be sampled.
Choosing an appropriate buffer size is not easy and it should be taken care not to select a value based on subjective interpretation of the study area characteristics.
